---
ptitle: "MA615 Final Project"
author: "Shixin Liang"
date: "12/15/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(psych)
library(GPArotation)
library(tidyverse)
library(readxl)
library(janitor)
library(magrittr)
library(GGally)
library(ggmosaic)
```


# Read Data 
```{r read data}
listing <- read.csv("listings.csv", header = TRUE)
review <- read.csv("reviews.csv", header = TRUE)
```  

# Plots  
## Part 1: Host
host_since 
host_response_time 
host_response_rate 
host_is_superhost 
host_has_profile_pic 
host_identity_verified 

```{r plot host_is_superhost}
# Data cleaning for host_is_superhost
listing$host_is_superhost <- as.character(listing$host_is_superhost)
listing <- filter(listing, listing$host_is_superhost!="")
listing$host_is_superhost[listing$host_is_superhost=="t"] <- "TRUE"
listing$host_is_superhost[listing$host_is_superhost=="f"] <- "FALSE"
listing$host_is_superhost <- as.factor(listing$host_is_superhost)

# plot host_is_superhost
superhost_plot <- ggplot(listing) +
 aes(x = host_is_superhost, fill = host_is_superhost) + 
 geom_bar() + 
 scale_fill_viridis_d() + 
 theme_minimal() + 
 labs(x = "Is Superhost?", y = "Frequency") + 
 ggtitle("Superhost Frequency") + 
 labs(caption = "Figure 1")
```
  
```{r plot host_since}
# Data cleaning for host_since
listing$host_since_year <- listing$host_since
listing$host_since_year <- as.Date(listing$host_since_year)
listing$host_since_year <- format(listing$host_since_year, "%Y")

# plot host_since
host_since_plot <- ggplot(listing) +
 aes(x = host_since_year) + 
 geom_bar(aes(fill = host_is_superhost)) + 
 scale_fill_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(x = "Host Begin Year", y = "Frequency") + 
 ggtitle("Host Begin Year Distribution") +
 labs(caption = "Figure 2")
``` 
  
```{r plot host_response_time}
# Data cleaning for host_response_time
listing$host_response_time[listing$host_response_time==""] <- NA
listing$host_response_time[listing$host_response_time=="N/A"] <- NA

# plot host_response_time
host_response_time_plot <- ggplot(listing) +
 aes(x = host_response_time) + 
 geom_bar(aes(fill = host_is_superhost)) + 
 scale_fill_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(x = "Host Response Time", y = "Frequency") + 
 ggtitle("Host Response Time Distribution") +
 labs(caption = "Figure 3")
```  
  
```{r plot host_response_rate}
# Data cleaning for host_response_rate
listing$host_response_rate <- as.character(listing$host_response_rate)
listing$host_response_rate[listing$host_response_rate==""] <- NA
listing$host_response_rate[listing$host_response_rate=="N/A"] <- NA
listing$host_response_rate <- as.factor(listing$host_response_rate)

host_response_rate_level <- levels(listing$host_response_rate)
host_response_rate_level <- host_response_rate_level[c(1,3:35,2)]
listing$host_response_rate <- factor(listing$host_response_rate, ordered = TRUE, levels = host_response_rate_level)

# plot host_response_rate
host_response_rate_plot <- ggplot(listing) +
 aes(x = host_response_rate) + 
 geom_bar(aes(fill = host_is_superhost)) + 
 scale_fill_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(x = "Host Response Rate", y = "Frequency") + 
 ggtitle("Host Response Rate Distribution") + 
 theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 10)) + 
 labs(caption = "Figure 4")
```  
  
```{r plot host_has_profile_pic}
# Data cleaning for host_has_profile_pic
listing$host_has_profile_pic <- as.character(listing$host_has_profile_pic)
listing <- filter(listing, listing$host_has_profile_pic!="")
listing$host_has_profile_pic[listing$host_has_profile_pic=="t"] <- "TRUE"
listing$host_has_profile_pic[listing$host_has_profile_pic=="f"] <- "FALSE"
listing$host_has_profile_pic <- as.factor(listing$host_has_profile_pic)

# Plot host_has_profile_pic
host_has_profile_pic_plot <- ggplot(listing) +
 aes(x = host_has_profile_pic) + 
 geom_bar(aes(fill = host_is_superhost)) + 
 scale_fill_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(x = "Host Has Profile Picture", y = "Frequency") + 
 ggtitle("Host Has Profile Picture Distribution") + 
 labs(caption = "Figure 5")
```  

```{r plot host_identity_verified}
# Data cleaning for host_identity_verified
listing$host_identity_verified <- as.character(listing$host_identity_verified)
listing <- filter(listing, listing$host_identity_verified!="")
listing$host_identity_verified[listing$host_identity_verified=="t"] <- "TRUE"
listing$host_identity_verified[listing$host_identity_verified=="f"] <- "FALSE"
listing$host_identity_verified <- as.factor(listing$host_identity_verified)

# plot host_identity_verified
host_identity_verified_plot <- ggplot(listing) +
 aes(x = host_identity_verified) + 
 geom_bar(aes(fill = host_is_superhost)) + 
 scale_fill_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(x = "Host Identity Verified", y = "Frequency") + 
 ggtitle("Host Identity Verified Distribution") + 
 labs(caption = "Figure 6")
```  
  
## Part 2: Listing
neighbourhood
room_type
accommodates
bathrooms
bedrooms
beds
bed_type

```{r plot neighbourhood}
# Data cleaning for neighbourhood
listing <- filter(listing, listing$neighbourhood!="")

# plot neighbourhood
neighbourhood_plot <- ggplot(listing) +
 aes(x = neighbourhood) + 
 geom_bar(aes(fill = host_is_superhost)) + 
 scale_fill_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(x = "Neighbourhood", y = "Frequency") + 
 ggtitle("Neighbourhood Distribution") + 
 theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 10)) + 
 labs(caption = "Figure 7")
```  

```{r plot room_type}
# plot room_type
room_type_plot <- ggplot(listing) +
  geom_mosaic(aes(x = product(host_is_superhost, room_type), fill=host_is_superhost), na.rm=TRUE) + 
  scale_fill_viridis_d(name="Is Superhost?") + 
  theme_minimal() +  
  labs(x = "Room Type", y = "Is Superhost?", title='Room Type Distribution')+
  theme(axis.text.x = element_text(hjust = 1, size=7)) + 
  labs(caption = "Figure 8")
```  

```{r plot accommodates}
# plot accommodates
accommodates_plot <- ggplot(listing) +
  geom_mosaic(aes(x = product(host_is_superhost, accommodates), fill=host_is_superhost), na.rm=TRUE) + 
  scale_fill_viridis_d(name="Is Superhost?") + 
  theme_minimal() +  
  labs(x = "Accommodates", y = "Is Superhost?", title='Accommodates Distribution')+
  theme(axis.text.x = element_text(hjust = 1, size=7)) + 
  labs(caption = "Figure 9")
```  

```{r plot bathrooms}
# plot bathrooms
bathrooms_plot <- ggplot(listing) +
  geom_mosaic(aes(x = product(host_is_superhost, bathrooms), fill=host_is_superhost), na.rm=TRUE) + 
  scale_fill_viridis_d(name="Is Superhost?") + 
  theme_minimal() +  
  labs(x = "Number of Bathrooms", y = "Is Superhost?", title='Number of Bathrooms Distribution')+
  theme(axis.text.x = element_text(hjust = 1, size=7)) + 
  labs(caption = "Figure 10")
```  

```{r plot bedrooms}
# plot bedrooms
bedrooms_plot <- ggplot(listing) +
  geom_mosaic(aes(x = product(host_is_superhost, bedrooms), fill=host_is_superhost), na.rm=TRUE) + 
  scale_fill_viridis_d(name="Is Superhost?") + 
  theme_minimal() +  
  labs(x = "Number of Bedrooms", y = "Is Superhost?", title='Number of Bedrooms Distribution')+
  theme(axis.text.x = element_text(hjust = 1, size=7)) + 
  labs(caption = "Figure 11")
```  

```{r plot beds}
# plot beds
beds_plot <- ggplot(listing) +
  geom_mosaic(aes(x = product(host_is_superhost, beds), fill=host_is_superhost), na.rm=TRUE) + 
  scale_fill_viridis_d(name="Is Superhost?") + 
  theme_minimal() +  
  labs(x = "Number of Beds", y = "Is Superhost?", title='Number of Beds Distribution')+
  theme(axis.text.x = element_text(hjust = 1, size=6)) + 
  labs(caption = "Figure 12")
```

```{r plot bed_type}
# plot bed_type
bed_type_plot <- ggplot(listing) +
 aes(x = bed_type) + 
 geom_bar(aes(fill = host_is_superhost)) + 
 scale_fill_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(x = "Bed Type", y = "Frequency") + 
 ggtitle("Bed Type Distribution") + 
 theme(axis.text.x = element_text(hjust = 1, size = 10)) + 
 labs(caption = "Figure 13")
```  


## Part 3: Price
price
security_deposit
cleaning_fee
extra_people

```{r plot price}
# Data cleaning for price
listing$price <- gsub('[$]','',listing$price) 
listing$price <- as.numeric(gsub(',','',listing$price)) 

# plot price
price_rating_plot <- ggplot(data = listing, aes(x = review_scores_rating, y = price)) +
 geom_point(aes(colour = host_is_superhost)) + 
 scale_colour_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(y = "Price", x = "Rating") + 
 ggtitle("Price vs. Rating") + 
 theme(axis.text.x = element_text(hjust = 1, size = 8)) +
 labs(caption = "Figure 14")

```  

```{r plot security_deposit}
# Data cleaning for security_deposit
listing$security_deposit <- gsub('[$]','',listing$security_deposit) 
listing$security_deposit <- as.numeric(gsub(',','',listing$security_deposit)) 

# plot security_deposit
security_deposit_rating_plot <- ggplot(data = listing, aes(x = review_scores_rating, y = security_deposit)) +
 geom_point(aes(colour = host_is_superhost)) + 
 scale_colour_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(y = "Security Deposit", x = "Rating") + 
 ggtitle("Security Deposit vs. Rating") + 
 theme(axis.text.x = element_text(hjust = 1, size = 8)) +
 labs(caption = "Figure 15")
``` 

```{r plot cleaning_fee}
# Data cleaning for cleaning_fee
listing$cleaning_fee <- gsub('[$]','',listing$cleaning_fee) 
listing$cleaning_fee <- as.numeric(gsub(',','',listing$cleaning_fee)) 

# plot cleaning_fee
cleaning_fee_plot <- ggplot(data = listing, aes(x = review_scores_rating, y = cleaning_fee)) +
 geom_point(aes(colour = host_is_superhost)) + 
 scale_colour_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(y = "Cleaning Fee", x = "Rating") + 
 ggtitle("Cleaning Fee vs. Rating") + 
 theme(axis.text.x = element_text(hjust = 1, size = 8)) +
 labs(caption = "Figure 16")
``` 
  
```{r plot extra_people}
# Data cleaning for extra_people
listing$extra_people <- gsub('[$]','',listing$extra_people) 
listing$extra_people <- as.numeric(gsub(',','',listing$extra_people)) 

# plot extra_people
extra_people_plot <- ggplot(data = listing, aes(x = review_scores_rating, y = extra_people)) +
 geom_point(aes(colour = host_is_superhost)) + 
 scale_colour_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(y = "Extra People Fee", x = "Rating") + 
 ggtitle("Extra People Fee vs. Rating") + 
 theme(axis.text.x = element_text(hjust = 1, size = 8)) + 
 theme(axis.text.y = element_text(hjust = 1, size = 6)) +
 labs(caption = "Figure 17")
``` 
  
  
## Part 4: Rules
minimum_nights
maximum_nights
cancellation_policy
require_guest_profile_picture  
  
```{r plot minimum_nights}
# plot minimum_nights
minimum_nights_plot <- ggplot(data = filter(listing, listing$minimum_nights<250 & listing$maximum_nights<250), aes(y = maximum_nights, x = minimum_nights)) +
 geom_point(aes(colour = host_is_superhost)) + 
 scale_colour_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(x = "Minimum Nights", y = "Maximum Nights") + 
 ggtitle("Minimum Nights vs. Maximum Nights") + 
 theme(axis.text.x = element_text(hjust = 1, size = 8)) +
 labs(caption = "Figure 18")
``` 

```{r plot cancellation_policy}
# plot cancellation_policy
cancellation_policy_plot <- ggplot(listing) +
  geom_mosaic(aes(x = product(host_is_superhost, cancellation_policy), fill=host_is_superhost), na.rm=TRUE) + 
  scale_fill_viridis_d(name="Is Superhost?") + 
  theme_minimal() +  
  labs(x = "Cancellation Policy", y = "Is Superhost?", title='Cancellation Policy Distribution')+
  theme(axis.text.x = element_text(angle = 30, hjust = 1, size=7)) + 
  labs(caption = "Figure 19")
``` 

```{r plot require_guest_profile_picture}
# Data cleaning for require_guest_profile_picture
listing$require_guest_profile_picture <- as.character(listing$require_guest_profile_picture)
listing$require_guest_profile_picture[listing$require_guest_profile_picture=="t"] <- "TRUE"
listing$require_guest_profile_picture[listing$require_guest_profile_picture=="f"] <- "FALSE"
listing$require_guest_profile_picture <- as.factor(listing$require_guest_profile_picture)

# plot require_guest_profile_picture
require_guest_profile_picture_plot <- ggplot(listing) +
  geom_mosaic(aes(x = product(host_is_superhost, require_guest_profile_picture), fill=host_is_superhost), na.rm=TRUE) +
  scale_fill_viridis_d(name="Is Superhost?") + 
  theme_minimal() +  
  labs(x = "Require Guest Profile Picture", y = "Is Superhost?", title='Require Guest Profile Picture Distribution')+
  theme(axis.text.x = element_text(hjust = 1, size=10)) + 
  labs(caption = "Figure 20")
``` 
  

## Part 5: Review
number_of_reviews
review_scores_rating
review_scores_accuracy
review_scores_cleanliness
review_scores_checkin
review_scores_communication
review_scores_location
review_scores_value
reviews_per_month

```{r plot number_of_reviews}
# calculate average number of reviews
avg_number_of_reviews <- aggregate(listing$number_of_reviews, list(listing$host_is_superhost), mean)

# plot average number of reviews
number_of_reviews_plot <- ggplot(data = avg_number_of_reviews, aes(x = Group.1, y = x, fill = Group.1)) + 
  geom_bar(stat="identity") +
  scale_fill_viridis_d(name="Is Superhost?") + 
  theme_minimal() + 
  labs(x = "Is Superhost?", y = "Number of Reviews") + 
  ggtitle("Number of Reviews Distribution") + 
  labs(caption = "Figure 21")
```  
  
```{r plot review_scores_rating}
# plot review_scores_rating
review_scores_rating_plot <- ggplot(data = listing, aes(x = review_scores_rating, y = number_of_reviews)) +
 geom_point(aes(colour = host_is_superhost)) + 
 scale_colour_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(y = "Number of Reviews", x = "Average Rating") + 
 ggtitle("Number of Reviews vs. Average Rating") + 
 theme(axis.text.x = element_text(hjust = 1, size = 8)) +
 labs(caption = "Figure 22")
```  
  
```{r plot review_scores_accuracy}
# plot review_scores_accuracy
review_scores_accuracy_plot <- ggplot(data = listing, aes(x = review_scores_rating, y = review_scores_accuracy)) +
 geom_point(aes(colour = host_is_superhost)) + 
 scale_colour_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(y = "Accuracy Rating", x = "Average Rating") + 
 ggtitle("Accuracy Rating vs. Average Rating") + 
 theme(axis.text.x = element_text(hjust = 1, size = 8)) +
 labs(caption = "Figure 23")
```  
  
```{r plot review_scores_cleanliness}
# plot review_scores_cleanliness
review_scores_cleanliness_plot <- ggplot(data = listing, aes(x = review_scores_rating, y = review_scores_cleanliness))+
 geom_point(aes(colour = host_is_superhost)) + 
 scale_colour_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(y = "Cleanliness Rating", x = "Average Rating") + 
 ggtitle("Cleanliness Rating vs. Average Rating") + 
 theme(axis.text.x = element_text(hjust = 1, size = 8)) +
 labs(caption = "Figure 24")
```  
  
```{r plot review_scores_checkin}
# plot review_scores_checkin
review_scores_checkin_plot <- ggplot(data = listing, aes(x = review_scores_rating, y = review_scores_checkin)) +
 geom_point(aes(colour = host_is_superhost)) + 
 scale_colour_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(y = "Checkin Rating", x = "Average Rating") + 
 ggtitle("Checkin Rating vs. Average Rating") + 
 theme(axis.text.x = element_text(hjust = 1, size = 8)) +
 labs(caption = "Figure 25")
```  
  
```{r plot review_scores_communication}
# plot review_scores_communication
review_scores_communication_plot <- ggplot(data = listing, aes(x = review_scores_rating, y = review_scores_communication)) +
 geom_point(aes(colour = host_is_superhost)) + 
 scale_colour_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(y = "Communication Rating", x = "Average Rating") + 
 ggtitle("Communication Rating vs. Average Rating") + 
 theme(axis.text.x = element_text(hjust = 1, size = 8)) +
 labs(caption = "Figure 26")
```  
  
```{r plot review_scores_location}
# plot review_scores_location
review_scores_location_plot <- ggplot(data = listing, aes(x = review_scores_rating, y = review_scores_location)) +
 geom_point(aes(colour = host_is_superhost)) + 
 scale_colour_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(y = "Location Rating", x = "Average Rating") + 
 ggtitle("Location Rating vs. Average Rating") + 
 theme(axis.text.x = element_text(hjust = 1, size = 8)) +
 labs(caption = "Figure 27")
```  

```{r plot review_scores_value}
# plot review_scores_value
review_scores_value_plot <- ggplot(data = listing, aes(x = review_scores_rating, y = review_scores_value)) +
 geom_point(aes(colour = host_is_superhost)) + 
 scale_colour_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(y = "Value Rating", x = "Average Rating") + 
 ggtitle("Value Rating vs. Average Rating") + 
 theme(axis.text.x = element_text(hjust = 1, size = 8)) +
 labs(caption = "Figure 28")
```  

```{r plot reviews_per_month}
# plot reviews_per_month
review_scores_rating_permonth_plot <- ggplot(data = listing, aes(x = reviews_per_month, y = number_of_reviews)) +
 geom_point(aes(colour = host_is_superhost)) + 
 scale_colour_viridis_d(name="Is Superhost?") + 
 theme_minimal() + 
 labs(y = "Number of Reviews", x = "Number of Reviews Per Month") + 
 ggtitle("Number of Reviews vs. Number of Reviews Per Month") + 
 theme(axis.text.x = element_text(hjust = 1, size = 8)) +
 labs(caption = "Figure 29")
```  

  
# Maps
latitude  
longitude  
  
```{r}  
library(knitr)
library(leaflet)
library(maps)
library(htmlwidgets)
library(tidyverse)
library(ggmap)
```  
  
```{r map slide}
# plot map for slide, showing locations of super hosts' listings and normal hosts' listings
boston <- get_map("boston", zoom=12)

host_is_superhost_map <- ggmap(boston ) + 
       geom_point(data=filter(listing, listing$host_is_superhost=="TRUE"), aes(x=longitude, y=latitude), color="#ED6664", size=1, alpha=0.5) + 
       geom_point(data=filter(listing, listing$host_is_superhost=="FALSE"), aes(x=longitude, y=latitude),           color="#388288", size=1, alpha=0.5)

```
  
```{r map shiny basic}
# plot map for shiny interaction
# built icons
icons <- awesomeIcons(
  icon = 'disc',
  iconColor = 'black',
  library = 'ion', # Options are 'glyphicon', 'fa', 'ion'.
  markerColor = "blue",
  squareMarker = TRUE
)

# plot map for shiny
map <- leaflet(data = listing) %>%
  setView(-71.10000, 42.32000, zoom = 11) %>% 
  addProviderTiles("CartoDB.Positron", group = "Map") %>%
  addProviderTiles("Esri.WorldImagery", group = "Satellite")%>% 
  addProviderTiles("Esri.WorldShadedRelief", group = "Relief")%>%
  addMarkers(~longitude, ~latitude, label = ~name, group = "Sites") %>%
  addScaleBar(position = "bottomleft") %>%
  addLayersControl(
    baseGroups = c("Map", "Satellite", "Relief"),
    overlayGroups = c("Sites"),
    options = layersControlOptions(collapsed = FALSE)
  )

# print it
invisible(print(map))
# saveWidget(map, file="Boston_Public_Library_Sites2.html", selfcontained=TRUE)
``` 
  
  
# Text Ming
name
description
comments

```{r name}
library(dplyr)

# get a name data frame
name_df <- listing[, c(5, 29)]
name_df$name <- as.character(name_df$name)

# break the text into individual tokens
library(tidytext)

name_df <- name_df %>%  
  group_by(host_is_superhost) %>%
  unnest_tokens(word, name)

name_df <- name_df %>%
  count(word, sort = TRUE) 

data(stop_words)

name_df <- name_df %>%
  anti_join(stop_words)


# a visualization of the most common words
name_df_superhost_frequency <- name_df  %>%
  filter(n > 50) %>%
  filter(host_is_superhost=="TRUE") %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()

name_df_not_superhost_frequency <- name_df  %>%
  filter(n > 120) %>%
  filter(host_is_superhost=="FALSE") %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()


# Sentiment analysis
library(tidytext)

# sentiment frequency: joy
nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

name_df_joy <- name_df %>%
  inner_join(nrc_joy) 

name_df_joy_superhost <- name_df %>%
  filter(n >= 10) %>%
  filter(host_is_superhost=="TRUE") %>%
  inner_join(nrc_joy) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()

name_df_joy_not_superhost <- name_df %>%
  filter(n >= 20) %>%
  filter(host_is_superhost=="FALSE") %>%
  inner_join(nrc_joy) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() 

# Wordclouds
data(stop_words)
library(wordcloud)

name_df_superhost_wordclouds <- name_df  %>%
  filter(host_is_superhost=="TRUE") %>%
  with(wordcloud(word, n, max.words = 200, colors=brewer.pal(8, "Dark2")))

name_df_not_superhost_wordclouds <- name_df  %>%
  filter(host_is_superhost=="FALSE") %>%
  with(wordcloud(word, n, max.words = 200, colors=brewer.pal(8, "Dark2")))
```  
  
  
```{r description}
# get a description data frame
description_df <- listing[, c(8, 29)]
description_df$description <- as.character(description_df$description)

# break the text into individual tokens
description_df <- description_df %>%  
  group_by(host_is_superhost) %>%
  unnest_tokens(word, description)

description_df <- description_df %>%
  count(word, sort = TRUE) 

description_df <- description_df %>%
  anti_join(stop_words)

# a visualization of the most common words
description_df_superhost_frequency <- description_df  %>%
  filter(n > 500) %>%
  filter(host_is_superhost=="TRUE") %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()

description_df_not_superhost_frequency <- description_df  %>%
  filter(n > 1000) %>%
  filter(host_is_superhost=="FALSE") %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()


# Sentiment analysis
# sentiment frequency: joy
description_df_joy <- description_df %>%
  inner_join(nrc_joy) 

description_df_joy_superhost <- description_df %>%
  filter(n >= 50) %>%
  filter(host_is_superhost=="TRUE") %>%
  inner_join(nrc_joy) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()

description_df_joy_not_superhost <- description_df %>%
  filter(n >= 100) %>%
  filter(host_is_superhost=="FALSE") %>%
  inner_join(nrc_joy) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() 

# Wordclouds
description_df_superhost_wordclouds <- description_df  %>%
  filter(host_is_superhost=="TRUE") %>%
  with(wordcloud(word, n, max.words = 200, colors=brewer.pal(8, "Dark2")))

description_df_not_superhost_wordclouds <- description_df  %>%
  filter(host_is_superhost=="FALSE") %>%
  with(wordcloud(word, n, max.words = 200, colors=brewer.pal(8, "Dark2")))
```  
  
  
# Review Text: comments  
```{r comments merch data}
# merge listing dataset and reviews dataset
listing_superhost <- listing[, c(1, 29)]
colnames(listing_superhost)[1] <- "listing_id"

review_df  <- list(review, listing_superhost) %>% reduce(full_join, by = "listing_id")
```  

```{r comments}
# get a description data frame
comments_df <- review_df[, c(6, 7)]
comments_df$comments <- as.character(comments_df$comments)
comments_df <- na.omit(comments_df)

# break the text into individual tokens
comments_df <- comments_df %>%  
  group_by(host_is_superhost) %>%
  unnest_tokens(word, comments)

comments_df <- comments_df %>%
  count(word, sort = TRUE) 

comments_df <- comments_df %>%
  anti_join(stop_words)

# a visualization of the most common words
comments_df_superhost_frequency <- comments_df  %>%
  filter(n > 9000) %>%
  filter(host_is_superhost=="TRUE") %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()

comments_df_not_superhost_frequency <- comments_df  %>%
  filter(n > 6000) %>%
  filter(host_is_superhost=="FALSE") %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()


# Sentiment analysis
# Most common positive and negative words for super hosts
comments_df_superhost_bing_word_counts <- comments_df %>%
  filter(host_is_superhost=="TRUE") %>%
  inner_join(get_sentiments("bing")) 

comments_df_superhost_bing_word_counts_positive <- comments_df_superhost_bing_word_counts  %>%
  filter(n > 5000) %>%
  filter(sentiment=="positive") %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill="#388288") +
  xlab(NULL) +
  labs(y = "Contribution to Positive Sentiment") + 
  coord_flip()

comments_df_superhost_bing_word_counts_negative <- comments_df_superhost_bing_word_counts  %>%
  filter(n > 250) %>%
  filter(sentiment=="negative") %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill="#ED6664") +
  xlab(NULL) +
  labs(y = "Contribution to Negative Sentiment") + 
  coord_flip()

# Most common positive and negative words for normal hosts
comments_df_not_superhost_bing_word_counts <- comments_df %>%
  filter(host_is_superhost=="FALSE") %>%
  inner_join(get_sentiments("bing")) 

comments_df_not_superhost_bing_word_counts_positive <- comments_df_not_superhost_bing_word_counts  %>%
  filter(n > 3000) %>%
  filter(sentiment=="positive") %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill="#388288") +
  xlab(NULL) +
  labs(y = "Contribution to Positive Sentiment") + 
  coord_flip()

comments_df_not_superhost_bing_word_counts_negative <- comments_df_not_superhost_bing_word_counts  %>%
  filter(n > 300) %>%
  filter(sentiment=="negative") %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill="#ED6664") +
  xlab(NULL) +
  labs(y = "Contribution to Positive Sentiment") + 
  coord_flip()


# Wordclouds
library(reshape2)

comments_df_superhost_wordclouds <- comments_df_superhost_bing_word_counts %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("#388288", "#ED6664"), max.words = 200)

comments_df_not_superhost_wordclouds <- comments_df_not_superhost_bing_word_counts %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("#388288", "#ED6664"), max.words = 200)

```  
  
  
  